Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-23 GWLDCII.tex
minor changes to penultimate intro para

This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics literature, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}. In this paper we give an algorithm to read off a combinatorial characterization (namely the Grassmann necklace, see Definition~\ref{def:grassmann necklace}) of the associated positroid cell from the Wilson loop diagram itself. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$-dimensional manifold in $\Gr(k,n)$.

>>>>

This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}. In this paper, we give an algorithm to read the Grassmann necklace, one of the standard combinatorial characterizations of the positroid cell, directly off the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$-dimensional manifold in $\Gr(k,n)$.
